Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-08 paper.tex
learning curve figure
added circuit figure

    (m)++(1.2,0) node [port] (l) {\textsc{MUX}$(x,y,z)$}
    ;
%% (0,0) node[and port] (myand2) {}
%% (2,1) node[xnor port] (myxnor) {}
%% (myand1.out) -- (myxnor.in 1)
%% (myand2.out) -- (myxnor.in 2);
  \end{circuitikz}
\caption{\system discovers the above multiplexer circuit, which it uses to make more complicated circuits like the one below.}\label{multiplexer}
  \end{figure}

@@

\begin{figure}\centering
  \includegraphics[width = 7cm]{figures/regression.eps}
  \caption{Learning curves for \system both with and without the recognition model (No NN in the above plots). Red: \system. Green: no neural network. Notice how the model without the neural network eventually solves almost all the tasks, but does so using programs with lower likelihood (see Table~\ref{regressionComparison}).}\label{regressionLearningCurve}  
\end{figure}

>>>>

    (m)++(1.2,0) node [port] (l) {\textsc{MUX}$(x,y,z)$}
    ;
%% (0,0) node[and port] (myand2) {}
%% (2,1) node[xnor port] (myxnor) {}
%% (myand1.out) -- (myxnor.in 1)
%% (myand2.out) -- (myxnor.in 2);
  \end{circuitikz}
  \begin{circuitikz} \draw
    (0,0) node[port] (a) {$a$}
    (a)++(0,-0.7) node[port] (b) {$b$}

    (a)++(1,-0) node[nand port, scale = 0.5] (ab1) {}
    (b)++(1,-0) node[nand port, scale = 0.5] (ab2) {}
    (ab1)++(1,-0.35) node[nand port, scale = 0.5] (o) {}

    (a.out) -| (ab1.in 1)
    (a.out) -| (ab1.in 2)
    (b.out) -| (ab2.in 1)
    (b.out) -| (ab2.in 2)

    (ab1.out) -- (o.in 1)
    (ab2.out) -- (o.in 2)

    (o)++(0.8,0) node [port] (l) {\textsc{OR}$(a,b)$}
    ;
  \end{circuitikz}
  \begin{circuitikz}     \node(m)[draw] at (1,-1) {MUX}; \draw
    (0,0) node[port] (w) {$w$}
    (w)++(0,-0.5) node[port] (x) {$x$}
    (x)++(0,-0.5) node[port] (y) {$y$}
    (y)++(0,-0.5) node[port] (z) {$z$}

    (z.out) -| (m.south)
    (y.out) -| (m.west)
    (x.out) -| (m.north)

    (y)++(2.5,0.13) node[or port, scale = 0.5] (z) {}
    (m.east) -- (z.in 2)
    (w.east) -| (z.in 1)
    ;
  \end{circuitikz}
\caption{\system discovers multiplexers (above) and OR gates (bottom left), which it uses to make more complicated circuits (bottom right), which it was unable to build without discovering these new primitives.}\label{multiplexer}
  \end{figure}

@@

\begin{figure}\centering
  \includegraphics[width = 7cm]{figures/regression.eps}
  \includegraphics[width = 7cm]{figures/textLearningCurve.eps}
  \includegraphics[width = 7cm]{figures/circuitLearningCurve.eps}  
  \caption{Learning curves for \system both with and without the recognition model (No NN in the above plots). Red: \system. Green: no neural network. Notice how the model without the neural network eventually solves almost all the tasks, but does so using programs with lower likelihood (see Table~\ref{regressionComparison}).}\label{regressionLearningCurve}  
\end{figure}
